An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-04 ex3/paper/paper.tex
Add 2015 accuracy

\begin{table}
% Evaluated using
% ./python learn.py --dataroot flows.pickle --net runs/Oct26_00-03-50_gpu/lstm_module_1284.pth --function test --batchSize 512
% ./python learn.py --dataroot flows15.pickle --net runs/Oct28_15-41-46_gpu/lstm_module_997.pth --function test --batchSize 512
% on Dec. 4th
\caption{Detection performance on a packet and flow level.} \label{tab:performance_results}
\centering
\begin{tabular}{l r r r r} \toprule
& \multicolumn{2}{c}{CIC-IDS-17} & \multicolumn{2}{c}{UNSW-NB-15} \\
	&	Packet	&	Flow	&	Packet	&	Flow	\\ \midrule
Accuracy	&	0.991	&	0.997	&		&		\\
Precision	&	0.970	&	0.997	&		&		\\
Recall	&	0.978	&	0.991	&		&		\\
F1	&	0.974	&	0.994	&		&		\\
Youden	&	0.972	&	0.990	&		&		\\

>>>>

\begin{table}
% Evaluated using
% ./python learn.py --dataroot flows.pickle --net runs/Oct26_00-03-50_gpu/lstm_module_1284.pth --function test --batchSize 512
% ./python learn.py --dataroot flows15.pickle --net runs/Oct28_15-41-46_gpu/lstm_module_997.pth --function test --batchSize 512
% on Dec. 4th
\caption{Detection performance on a packet and flow level.} \label{tab:performance_results}
\centering
\begin{tabular}{l r r r r} \toprule
& \multicolumn{2}{c}{CIC-IDS-17} & \multicolumn{2}{c}{UNSW-NB-15} \\
	&	Packet	&	Flow	&	Packet	&	Flow	\\	\midrule
Accuracy	&	0.991	&	0.997	&	0.995	&	0.983	\\	
Precision	&	0.970	&	0.997	&	0.834	&	0.786	\\	
Recall	&	0.978	&	0.991	&	0.876	&	0.726	\\	
F1	&	0.974	&	0.994	&	0.855	&	0.755	\\	
Youden	&	0.972	&	0.990	&	0.873	&	0.719	\\
